---
title: "Week_3"
output: pdf_document
date: "2022-10-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("Week_3.R")
```

# Q1

Simulate (s,S) inventory system using the calling sequence below.

```{r}
set.seed(12345)
Y <- MySim(123, 2000, 55555)

### calculate 95% confidence intervals for point estimates
# mean
mean_95 <- c(mean(Y) + qnorm(0.975)*sd(Y)/length(Y),mean(Y) - qnorm(0.975)*sd(Y)/length(Y))
# 80% quantile
l_hat <- floor(length(Y)*0.8 - qnorm(0.975)*sqrt(length(Y)*0.8*(1-0.8)))
u_hat <- ceiling(length(Y)*0.8 + qnorm(0.975)*sqrt(length(Y)*0.8*(1-0.8)))
# prob Y>=210
prob_95 <- (length(Y)/(length(Y)-1))*sum(Y>=210)/length(Y)*(1-sum(Y>=210)/length(Y))
```

Using 2000 replications, the estimates are:

-   mean: `r mean(Y)`

-   standard deviation: `r sd(Y)`

-   80th percentile of average cost: `r quantile(Y,probs=c(0.8))`

-   probability that cost is greater than or equal to \$210: `r sum(Y>=210)/length(Y)`

-   95% confidence intervals on your point estimates:
    - mean: (`r mean_95`)
    - 80th percentile: $[Y_{(1564)},Y_{(1636)}]$
    - probability that cost is greater than or equal to \$210: ???

# Q2

Calculate MSER statistic in the tandem queue system.

```{r}

```
